%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3.5cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{BhanuPrakashPoluparthi} % Your first name
%\familyname{Poluparthi} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
%\address{Address}{City, State Zip}
\mobile{(+91) 9985389370}
\email{p.bhanuprakash12345@gmail.com}
\homepage{www.linkedin.com/in/bhanu-prakash-22659015b} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\homepage{https://sites.google.com/view/sikka-anmol/home}{Homepage}
\extrainfo{DOB: April 7, 1999}
%\photo[70pt][0.4pt]{pictures/House} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2017--2021}{B Tech}{}{}{\textit{Department of Computer Science, \link[Amrita Vishwa Vidyapeetham]{https://www.amrita.edu/}, Amritapuri, Kerala, India, \textbf{CGPA}: 9.39}}{}

\cventry{2016-2017}{Intermediate}{}{}{\textit{\link[FIITJEE Junior College]{http://www.fiitjeehyd.com/Kukatpally/CenterHome.aspx}, Hyderabad, Telangana, India \textbf{Percentage}:96.4\%}}{}

\cventry{2015}{Matriculation}{}{}{\textit{\link[Sri Chaitanya High School]{https://srichaitanyaschool.net/}, Hyderabad, Telangana, India CGPA 10.0}}{}


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------


% \renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists
% \cvlistdoubleitem{Piano}{}
% \cvlistitem{Baseball}

%----------------------------------------------------------------------------------------
%	Achievements SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cvitem{Feb 2019 - Present}{\textbf{GirlScipt Summer of Code}, Mentor}

\cvitem{}{\link[\textit{Groot}]{https://github.com/omi10859/groot} is a open-source assistance made to make virtual life fun and easy. It can perform many tasks like opening a website, playing music video or any video on YouTube over voice command and much more. It's a platform-independent so you can use it on mac, windows or Linux. Mentored students regarding the project tasks.}

\cvitem{Nov 2018 - Jan 2019}{\textbf{KWoC}, Developer}
\cvitem{}{Developer at \link[\textit{Kharagpur Winter of Code 2018}]{https://drive.google.com/open?id=1RiP3VCXVm0CJV3Wxf0og67-2k9UoGgJR} \link[Physics-engine]{https://github.com/MUKESHSIHAG/physics-simulation} is a simple physics engine module made using pygame in python. It is based on physics phenomenons and mathematical expressions like vectors and angles, simulated according to the calculations and requirements.}

\cvitem{Oct 2018 - Dec 2018} {\link[\textbf{Google Code-In}]{https://drive.google.com/open?id=1hFgn-3EUnpt52Sg5QooFV4DOIOaaNJLP}, Mentor, Drupal}

\cvitem{}{Monitor and manage various tasks for Google code-In(GCI) 2018 for students under 18. Active interaction with students regarding tasks and reviewing the tasks submitted. I had to assure and maintain quality among the work done by the students in the community.}

\cvitem{April 2018 - Jun 2018}{\textbf{Google Summer of Code}, Developer Intern, Drupal}
\cvitem{}{Port \textit{Commerce Instamojo} module to Drupal 8 from Drupal 7. Commerce Instamojo is a payment gateway that allows users to execute payments through links. Payment, refund and customer details forms converted to Drupal 8 configuration. Payment gateway functions ported to Drupal 8 configuration. }



%----------------------------------------------------------------------------------------
%	Open Source SECTION
%----------------------------------------------------------------------------------------
\section{Open Source Contributions}
\cvitem{}{\textbf{Drupal},\textit{Developer}}
\cvitem{}{Active member, contributor and developer with Drupal, an Open Source software that includes a Content Management System and a development framework built on PHP and Javascript. Contribution Tracker: \link[Bhanu Prakash]{https://www.drupal.org/u/bhanuprakashnani}}


%----------------------------------------------------------------------------------------
%	Projects SECTION
%----------------------------------------------------------------------------------------

\section{Projects}
\cvitem{Nov 2018}{\textbf{Resume Builder}}
\cvitem{}{A java based Resume Builder that creates a resume file taking information through responsive User Interface forms, made by using Swings. Uses Java Database Connectivity API for storing the intermediate information from fields and forms.}

\cvitem{Jan 2018}{\textbf{Field Collection Table}}
\cvitem{}{To port Field Collection Table module from Drupal 7 to Drupal 8 configuration. Field Collection Table provides a table formatter for the Field Collection Module which in hand provides a collection field with the feature of attaching any number of fields to it. A field collection is internally represented as an entity, which is embedded in the host entity. Thus, if desired field collections may be viewed and edited separately too.}

%----------------------------------------------------------------------------------------
%	Workshops / Hackathons SECTION
%----------------------------------------------------------------------------------------

\section{Conferences / Hackathons}

\cvitem{Dec 2018}{\textbf{Dev'Rel Conference}, Attendee | Bangalore, India}
\cvitem{}{An event aiming at the assimilation of developers advocates of multiple organisations, sharing their knowledge and experiences.}
\cvitem{Dec 2018}{\textbf{Hacko 1.0 Hackathon}, Participant | Bangalore, India}
\cvitem{}{Developed a Web application that automates the experience for customers in the insurance industries to check the different types of insurances applied and claimed. Increases the trust factor in the customers through this feature.}
\cvitem{Jan 2019}{\textbf{IHACK Hackathon}, Participant | IIT MUMBAI, India}
\cvitem{}{Developed a neural network model that classifies different classes of items from Depth Images and RGB images using Tensorflow and Python. Integrated with an Android app named TensorflowClassify.}
%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\section{Technical Skills}
%
\cvitem{Programming}{\textsc{Python, Java, PHP, C, SQL, Shell Scripting, Command Line}}

\cvitem{Platforms}{\textsc{Linux, Windows}}

\cvitem{Web Development}{\textsc{FrontEnd- HTML, CSS, Bootstrap, Javascript}}

\cvitem{}{ \textsc{BackEnd- Python, Django}}

\cvitem{Tools}{\textsc{Git, Docker, Latex}}

\cvitem{Editing}{\textsc{Adobe Premiere Pro}}

%----------------------------------------------------------------------------------------
%	Coursework SECTION
%----------------------------------------------------------------------------------------

\section{Coursework}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvitem{Core Courses}{Discrete Mathematics, Database Management Systems, Data Structure, Object Oriented Programming, Digital Systems and Electronics, Advance Engineering Mathematics, Computer Organization and Architecture, Operating Systems}


\cvitem{Lab Courses}{Data Structure Lab, Object Oriented Programming using JAVA Lab, Digital Electronics Lab, Operating System Lab}

%----------------------------------------------------------------------------------------
%	Achievements SECTION
%----------------------------------------------------------------------------------------
\section{Achievements}

\cvitem{2007}{NCO Olympiad \textbf{Gold Medallist}(National)}
\cvitem{2007}{English Olympiad Gold Medallist \textbf{Macmillan University}}
\cvitem{2008}{UCMAS - Arithmetic Maths \textbf{Gold Medallist}}
\cvitem{2009}{\textbf{Guinness World Record}(Group) Largest Canvas painting}
\cvitem{2009}{Prathmik Hindi Pariksha, \textbf{Statewide Distinction}}
\cvitem{2010}{National Biology Olympiad, \textbf{National Rank 9}}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Hindi}{Fluent}{}
\cvitemwithcomment{Telugu}{Fluent}{}
\cvitemwithcomment{German}{Basic}{Basic words and phrases only}
%\cvitemwithcomment{Dutch}{Basic}{}


\end{document}



